Software Citation Principles

### 2016-03-22 sc-principles/software-citation-principles.tex
adding new member who got missed
fixing two typos as explained in issue 79

Most noteable of the community efforts are those of WSSSPE~\cite{wssspe} and
SSI~\cite{ssi-workshops} who between them have run a series of workshops aimed
at gathering together community members with an interest in improving the
status of software in academia. \asnote{Not sure this is a sufficient one-line
summary but couldn't think of anything better.} In each of the three years that
WSSSPE workshops have run thus far, the participants have produced a report
documenting the topics covered. Section 5.8 and Appendix J in \cite{WSSSPE3}
has some preliminary work and discussion particularly relevant to this working
group.

@@

The goals of software include the linked ideas of crediting those responsible for software and understanding the dependencies of scientific products on specific software.
In the Importance principle (\ref{principle:importance}), we state that
``software should be cited whenever and wherever a research product (such as a paper or derived software) relies upon it, specifically, as part of the standard reference list for that research product.''
In the case of one code that is derived from another code, citing the derived software may appear to not credit those responsible for the original software, nor recognize its role in the work that used the derived software.
However, this is really analogous to how any research builds on other research, where each research product just cites those products that it directly builds on, not those that it indirectly builds on.
Understanding these chains of knowledge and credit have been part of history of science field for some time, though more recent work is suggesting more nuanced evaluation of the credit chains~\cite{casrai-credit, transitive_credit_json-ld}.

@@

>>>>

Most notable of the community efforts are those of WSSSPE~\cite{wssspe} and
SSI~\cite{ssi-workshops} who between them have run a series of workshops aimed
at gathering together community members with an interest in improving the
status of software in academia. \asnote{Not sure this is a sufficient one-line
summary but couldn't think of anything better.} In each of the three years that
WSSSPE workshops have run thus far, the participants have produced a report
documenting the topics covered. Section 5.8 and Appendix J in \cite{WSSSPE3}
has some preliminary work and discussion particularly relevant to this working
group.

@@

The goals of software include the linked ideas of crediting those responsible for software and understanding the dependencies of scientific products on specific software.
In the Importance principle (\ref{principle:importance}), we state that
``software should be cited whenever and wherever a research product (such as a paper or derived software) relies upon it, specifically, as part of the standard reference list for that research product.''
In the case of one code that is derived from another code, citing the derived software may appear to not credit those responsible for the original software, nor recognize its role in the work that used the derived software.
However, this is really analogous to how any research builds on other research, where each research product just cites those products that it directly builds on, not those that it indirectly builds on.
Understanding these chains of knowledge and credit have been part of the history of science field for some time, though more recent work is suggesting more nuanced evaluation of the credit chains~\cite{casrai-credit, transitive_credit_json-ld}.

@@

Jay Jay Billings, Oak Ridge National Laboratory
